# Exploratory data analysis

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/setup.R"))
```

### *Data Description*
#### *Table 1*
```{r}
userdataset <- read.csv(here::here("data/users.dataset.public.csv"))

```

```{r}
#missing value
check_na <- sum(is.na(userdataset))
check_na
```
#kable
```{r}
head(userdataset)
```

```{r}
# replace some columns' type, can see the info clearer in the summary 
userdataset[,2] <- as.character(userdataset[,2])
userdataset[,"country"]<- as.factor(userdataset[,"country"])
userdataset[,"hasAnyApp"]<- as.factor(userdataset[,"hasAnyApp"])
userdataset[,"gender"]<- as.factor(userdataset[,"gender"])
userdataset[,"hasAndroidApp"]<- as.factor(userdataset[,"hasAndroidApp"])
userdataset[,"hasIosApp"]<- as.factor(userdataset[,"hasIosApp"])

summary(userdataset[,-1])
```

```{r}

```

#char
# check mosaic, creat all characters then combine all


#p.country <- ggplot(data= c.country)+
#  geom_mosaic(aes(x = country), fill= country_number)

```{r}

c.country <- userdataset %>% 
  group_by(country) %>%
  summarise(country_number = n())

```

```{r}
 p.country <- ggplot(data = c.country,aes(x = country_number, 
                                          y = country))+
  geom_col()
p.country

```

# boolen

```{r}
# library(ggmosaic) add it to setup

# maybe not suit for this dataset 
gender_hasapp <- ggplot2::ggplot(data= userdataset)+
  geom_mosaic(aes(x = userdataset$hasAnyApp, conds = userdataset$gender, fill= hasIosApp))

gender_hasapp 
```

# numric
# box chart 
```{r}

```

#ggpair
#pca (option)