# Exploratory data analysis

```{r, echo = FALSE, message = FALSE}
source(here::here("scripts/setup.R"))
```

```{r}
install.packages("summarytools")
library(summarytools)
library(DataExplorer)
```

## Data inspection

### Data check

```{r}
str(userdataset)
summary(userdataset)

print(dfSummary(userdataset,style="grid",
                plain.ascii = FALSE, 
                tmp.img.dir = "/tmp",
                graph.magnif = 0.8),
      method = "render")

```

### Data modification

we will using graphics and visualizations to explore and analyze the dataset (EDA) first and to see if we need to combine with another dataset (named: Buyers-repartition-by-country ), to try to link with user's country, topbuyers and other variables.

### Data Attribute Modification

```{r}
# Replace some columns' type
userdataset[,2] <- as.character(userdataset[,2])
userdataset[,"country"]<- as.factor(userdataset[,"country"])
userdataset[,"hasAnyApp"]<- as.factor(userdataset[,"hasAnyApp"])
userdataset[,"gender"]<- as.factor(userdataset[,"gender"])
userdataset[,"hasAndroidApp"]<- as.factor(userdataset[,"hasAndroidApp"])
userdataset[,"hasIosApp"]<- as.factor(userdataset[,"hasIosApp"])

summary(userdataset[,-1])
###difference between 'summary(userdataset)' and 'summary(userdataset[,-1])' is lack "index".

# Delete the duplicate colums
###删除useless的元数据"identifierHash","type"; 删除重复列"country", "seniorityAsYears", "seniorityAsMonths", "civilityGenderId"。
userds <- userdataset[,!colnames(userdataset) %in% c("identifierHash","type","country","seniorityAsYears","seniorityAsMonths", "civilityGenderId") ]

```

```{r}

```


## Data description by using descriptive statistics and graphs

### Graphs for numeric variables

```{r}

```

### Graphs for non-numeric variables

```{r}

```

## Examination of the relationship between variables




* Mapping out the underlying structure
* Identifying the most important variables
* Univariate visualizations
* Multivariate visualizations
* Summary tables